Population Inference of Non-Spinning Eccentric Binary Black Holes

### 2023-06-09 paper/paper.tex
Inference tables
Updates from Overleaf

\begin{table*}[]
    \centering
    \begin{tabular}{|ccccccc|}
        \hline
        $\sigma_\epsilon$ & $m^1_{min} [M_\odot] $ & $m^1_{max} [M_\odot]$ & $m^2_{min} [M_\odot]$ & $m^2_{max} [M_\odot]$ & $\epsilon_{min}$ & $\epsilon_{max}$\\ \hline
        0.05 & 16.81 & 49.81 & 10.8 & 46.82 & 0.01 & 0.05\\ \hline
        0.1 & 19.03 & 49.93 & 10.1 & 48.64 & 0.05 & 0.1\\ \hline
        0.15 & 10.04 & 49.9 & 10.01 & 49.2 & 0.1 & 0.15\\ \hline
        0.2 & 19.6 & 49.97 & 10.73 & 48.39 & 0.15 & 0.2\\ \hline
    \end{tabular}
    \caption{Weighted Population Properties}
    \label{tab:pop_prop}
\end{table*}

@@

\begin{table*}[]
    \centering
    \begin{tabular}{|ccccccc|}
        \hline
        $\sigma_\epsilon$ & $m^1_{min} [M_\odot] $ & $m^1_{max} [M_\odot]$ & $m^2_{min} [M_\odot]$ & $m^2_{max} [M_\odot]$ & $\epsilon_{min}$ & $\epsilon_{max}$\\ \hline
        0.05 & 16.68 & 49.64 & 10.77 & 46.75 & 0.01 & 0.05\\ \hline
        0.1 & 18.95 & 49.51 & 9.89 & 48.33 & 0.05 & 0.1\\ \hline
        0.15 & 9.13 & 49.55 & 9.1 & 49.11 & 0.1 & 0.15\\ \hline
        0.2 & 18.2 & 49.79 & 10.3 & 47.08 & 0.15 & 0.2\\ \hline
    \end{tabular}
    \caption{Scaled Population Properties}
    \label{tab:popscl_prop}
\end{table*}

@@

\section{Results}

we can discuss the corner plots here.

@@

\includegraphics[width=0.95\textwidth]{paper/figures/corfig_0.05.png}
\caption{\label{fig:pop3d05}\textbf{Corner Plots for EBBHs and BBHS with $\sigma_\epsilon=0.05$}}

@@

\includegraphics[width=0.95\textwidth]{paper/figures/corfig_0.2.png}
\caption{\label{fig:pop3d05}\textbf{Corner Plots for EBBHs and BBHs with $\sigma_\epsilon=0.2$}}

>>>>

\begin{table*}[]
    \centering
    \begin{tabular}{c|cccccc}
        \hline
        Populations & $m^1_{min} [M_\odot] $ & $m^1_{max} [M_\odot]$ & $m^2_{min} [M_\odot]$ & $m^2_{max} [M_\odot]$ & $\epsilon_{min}$ & $\epsilon_{max}$\\ \hline
        First 1 & 16.81 & 49.81 & 10.8 & 46.82 & 0.01 & 0.05\\ \hline
        Second 2 & 19.03 & 49.93 & 10.1 & 48.64 & 0.05 & 0.1\\ \hline
        Third 3 & 10.04 & 49.9 & 10.01 & 49.2 & 0.1 & 0.15\\ \hline
        Forth 4 & 19.6 & 49.97 & 10.73 & 48.39 & 0.15 & 0.2\\ \hline
    \end{tabular}
    \caption{Weighted Population Properties}
    \label{tab:pop_prop}
\end{table*}

@@

\begin{table*}[]
    \centering
    \begin{tabular}{c|cccc}
        \hline
        Populations & $m^1_{min} [M_\odot] $ & $m^1_{max} [M_\odot]$ & $m^2_{min} [M_\odot]$ & $m^2_{max} [M_\odot]$ \\ \hline
        First & 16.68 & 49.64 & 10.77 & 46.75 \\ \hline
        Second & 18.95 & 49.51 & 9.89 & 48.33 \\ \hline
        Third & 9.13 & 49.55 & 9.1 & 49.11  \\ \hline
        Forth & 18.2 & 49.79 & 10.3 & 47.08  \\ \hline
    \end{tabular}
    \caption{Scaled Population Properties}
    \label{tab:popscl_prop}
\end{table*}

@@

\section{Population Inference}

\begin{table*}[]
    \centering
    \begin{tabular}{c|ccccc}
        \hline
       Inference & $log_{10}(\frac{\mathcal{R}}{Gpc^{-3}yr^-1})$ & $\alpha$ & $m_{min} [M_\odot] $ & $m_{max} [M_\odot]$ & $\sigma_\epsilon$ \\ \hline
      First& $1.88^{+0.18}_{-0.59}$ & $-1.41^{+1.29}_{-0.97}$ & $5.47^{+1.74}_{-1.74}$ & $69.67^{+10.20}_{-10.75}$ & $0.05^{+0.35}_{-0.02}$ \\ \hline
      Second & $1.89^{+0.15}_{-0.56}$ & $-0.99^{+1.01}_{-0.85}$ & $5.52^{+1.75}_{-1.80}$ & $69.74^{+10.64}_{-10.95}$ & $0.07^{+0.33}_{-0.02}$ \\ \hline
      Third & $1.90^{+0.14}_{-0.53}$ & $-0.94^{+0.94}_{-0.82}$ & $5.63^{+2.02}_{-1.92}$ & $69.73^{+10.92}_{-11.07}$ & $0.10^{+0.30}_{-0.02}$  \\ \hline
      Forth & $1.91^{+0.18}_{-0.55}$ & $-1.89^{+1.44}_{-1.00}$ & $5.48^{+1.87}_{-1.90}$ & $69.26^{+11.43}_{-10.96}$ & $0.14^{+0.29}_{-0.03}$  \\ \hline
    \end{tabular}
    \caption{Population Inference for EBBHs}
    \label{tab:inference_EBBHS}
\end{table*}

\begin{table*}[]
    \centering
    \begin{tabular}{c|cccc}
        \hline
        Inference & $log_{10}(\frac{\mathcal{R}}{Gpc^{-3}yr^-1})$ & $\alpha$ & $m_{min} [M_\odot] $ & $m_{max} [M_\odot]$ \\ \hline
      First & $1.89^{+0.17}_{-0.43}$ & $-1.68^{+1.08}_{-0.80}$ & $5.49^{+2.38}_{-2.41}$ & $68.83^{+14.66}_{-13.13}$  \\ \hline
      Second & $1.89^{+0.13}_{-0.43}$ & $-0.90^{+0.72}_{-0.68}$ & $5.40^{+2.29}_{-2.40}$ & $68.61^{+14.69}_{-13.33}$  \\ \hline
      Third & $1.89^{+0.13}_{-0.44}$ & $-0.57^{+0.65}_{-0.67}$ & $5.72^{+2.48}_{-2.40}$ & $68.74^{+14.30}_{-12.99}$   \\ \hline
      Forth & $1.89^{+0.14}_{-0.45}$ & $-1.20^{+0.81}_{-0.71}$ & $5.32^{+2.33}_{-2.38}$ & $68.83^{+14.51}_{-12.95}$  \\ \hline
    \end{tabular}
    \caption{Population Inference for NEBBHs}
    \label{tab:inference_NEBBHS}
\end{table*}
we can discuss the corner plots here.

@@

\includegraphics[width=0.95\textwidth]{paper/figures/corfig_0.05.png}
\caption{\label{fig:pop3d05}\textbf{Corner Plots for EBBHs and BBHS for $\sigma_\epsilon=0.05$}}

@@

\includegraphics[width=0.95\textwidth]{paper/figures/corfig_0.2.png}
\caption{\label{fig:pop3d05}\textbf{Corner Plots for EBBHs and BBHs for $\sigma_\epsilon=0.2$}}
